\class : Week \psetnum

### 2022-10-12 541_ism/week2/solutions.tex
541 - finish week 2 problems

\answer{}

>>>>

\answer{
    The rate at which we collect dust grains will be given by the usual form of
    \begin{equation}
        \mathcal{R} = n \sigma v
    \end{equation}
    We are given a collecting area, $A$, which corresponds to the cross section and velocity, $v_{\rm W}$, so those parts are easy. The more complicated part is that we need to know the number density of the ISM dust particles.\\

    \noindent Luckily for us, the problem from last week is going to be rather relevant! So we can apply what we did in the first parts of last week's problem set
    \begin{align}
        \rho_{\rm ISM} &= 1.4 m_p \cdot n_{\rm H} \\
        \rho_{\rm dust} &= 0.005 \rho_{\rm ISM} \\
        m_{\rm dust, particle} &= \frac{4}{3} \pi a^3 \cdot \rho_{\rm dust, particle} \\
    \end{align}
    Then we can use these things to get the number density of dust
    \begin{align}
        n_{\rm dust} &= \frac{\rho_{\rm dust}}{m_{\rm dust, particle}} \\
                     &= \frac{0.005 \cdot 1.4 m_p \cdot n_{\rm H}}{\frac{4}{3} \pi a^3 \cdot \rho_{\rm dust, particle}} \\
        n_{\rm dust} &= 3.1 \times 10^{-13} \unit{cm^{-3}}
    \end{align}
    Now we can use this to find the required area to get a rate of 1 particle per hour
    \begin{equation}
        \boxed{ A = \frac{\mathcal{R}}{n_{\rm dust} v_W} = \frac{1 \unit{hr^{-1}}}{3 \times 10^{-13} \unit{cm^{-3}} \cdot 26 \unit{km}{s^{-1}}} = 350 \unit{cm^2} }
    \end{equation}

}
